Simulation of Congenital Heart Defect Corrective Surgeries Using Thin Shell Elements

### 2012-03-02 Doc/Miccai/introduction.tex
small modif in the intro
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@389 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

In this paper we present an improved approach using a simulation model solely based on elastic thin shell elements. Our method is not limited to well-formed blood vessels and captures all low-level procedures necessary for aortoplasty. We use a relaxation process to arbitrarily join or attach blood vessels and patches without using springs that would add surplus energy to the physical system. By taking the overall tubular structure of blood vessels into consideration during generation of thin shell elements we achieve reasonable speed of the simulation.

>>>>

In this paper we present an improved approach for predictive simulation of congenital heart defect (CHD) corrective surgeries using a physics based model of the vessel walls: their mechanical behavior is simulated using elastic thin shell elements. 
Our method is not limited to well-formed blood vessels and captures all low-level procedures necessary for aortoplasty. We use a relaxation process to arbitrarily join or attach blood vessels and patches without using springs that would add surplus energy to the physical system. By taking the overall tubular structure of blood vessels into consideration during generation of thin shell elements we achieve reasonable speed of the simulation.
